Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Abstract tweaks and wordsmithing

\begin{abstract}
Abstracting abstract machines has recently been proposed as a
lightweight approach to designing sound and computable program
analyses.  The approach involves deriving abstract interpreters from
existing machine semantics and has been applied to a variety of
languages with features widely considered difficult to analyze.
Although analyzers are straightforward to build under this approach,
the result is prohibitively inefficient.

This article contributes a step by step process for going from a
\naive analyzer derived under the abstracting abstract machine
approach, to an efficient program analyzer.  The end result of the
process is a two to three order-of-magnitude improvement over the
systematically derived analyzer, making it competitive with
hand-optimized implementations that compute fundamentally less precise
results.
\end{abstract}

>>>>

\begin{abstract}
Abstracting abstract machines has been proposed as a
lightweight approach to designing sound and computable program
analyses.  The approach derives abstract interpreters from
existing machine semantics and has been applied to a variety of
languages with features widely considered difficult to analyze.
Although sound analyzers are straightforward to build under this approach,
they are also prohibitively inefficient.

This article contributes a step-by-step process for going from a
\naive{} analyzer derived under the abstracting abstract machine
approach to an efficient program analyzer.  The end result of the
process is a two to three order-of-magnitude improvement over the
systematically derived analyzer, making it competitive with
hand-optimized implementations that compute fundamentally less precise
results.
\end{abstract}
